\documentclass[10pt,a4paper]{article}

\usepackage[compact]{titlesec}

\newcommand{\hr}{\noindent\line(1,0){400}}
% \newcommand{\hr}{}
\newcommand{\br}{\hfill\\}
\newcommand{\CPP}{C\nolinebreak\hspace{-.05em}\raisebox{.5ex}{\tiny\textbf{++}}}
\newcommand{\CS}{C\nolinebreak\hspace{-.05em}\raisebox{.6ex}{\scriptsize\textbf\#}}

\setlength{\topmargin}{0in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{9.3in}
\setlength{\textwidth}{6.4in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}

\begin{document}
\noindent{\LARGE\textbf{En-Jan Chou}}
\vskip 0.05in
\noindent{zhouer@gmail.com}\\
\noindent{+1-713-410-3275}
% \noindent{7900 Cambridge Street,\\Apartment 11-1E,\\Houston, TX 77054}

\hr
\section*{Skills \& Expertise}
\vskip 0.05in
\begin{description}
\itemsep 0pt
\item[C] Advanced, 10 years experience.
\item[Python] Advanced, 3 years experience.
\item[Go] Advanced, 3 years experience.
\item[Javascript] Intermediate, 3 years experience.
\item[\CPP] Intermediate, 3 years experience.
\item[Blockchain] Advanced, 5 years experience.
\item[Linux/FreeBSD] Advenced, 5 years experience.
% \item[Java] Intermediate, 2 years experience.
% \item[\CS] Basic, 1 year experience.
\end{description}

\hr
\section*{Experience}
\begin{description}

\item[Senior Backend Engineer at Bincentive Inc.]
April 2019 -- Present\br
\textbf{Market Making} a cross-market cryptocurrency arbitrage system.\br
\textbf{Mirror Trade} a trading system trades cryptocurrency on behave of clients according to professional traders' trading signals.\br
I responsible for designing and implement the trading system and building the CI/CD environment.

\item[Systems Architect at DiQi Inc.]
September 2014 -- March 2019\br
\textbf{Pallet} is a smart contract system featuring scalability, and inter-blockchain operability.\br
\textbf{Gcoin} is a consortium blockchain system featuring multi-currency, high throughput, and governance.\br
I responsible for designing system architecture and doing research on blockchain related technologies.

\item[Software Engineer at CloudMosa Inc.]
June 2011 -- November 2011\br
\textbf{Puffin browser} is a cloud based remote browser.
I responsible for server-side development, including rendering server upgrading, porting, and Java applet rendering.

\item[Software Engineer at Cyberlink Corp.]
September 2008 -- April 2011\br
\textbf{PowerDVD 9, 10, 11} I responsible for software maintenance, developments, and refactoring.
Including multimedia playback, Win32 programming, Python GUI framework designing and manipulation.\br
\textbf{Software tamper resistance} I responsible for Blu-ray disc playback, managed copy, BD+ protection system architecture designing and implementation.

\item[Teaching Assistant at National Taiwan University]
September 2005 -- January 2006\br
\textbf{Computer Programming} I responsible for grading assignments, labs, and giving lectures.

\item[Network Administrator at National Central University]
September 2003 -- August 2004\br
\textbf{Network administration} I responsible for WWW, Mail, FTP, DNS, NFS, NIS, Gopher server administration, and network administration.
\end{description}

\hr
\section*{Projects}
\begin{description}
\item[Praline]\br
\textbf{Praline} is an open source Raspberry Pi based Bitcoin hardware wallet.

\item[Mickle]\br
\textbf{Mickle} is a P2P file sharing website. The browsers can exchange data directly through WebRTC.

\item[KeyTurbine]\br
\textbf{KeyTurbine} is a keyboard adapter which translates PS/2 signals into USB signals, enables key remapping, macro playing and USB NKRO handling.
I designed and made the hardware, firmware from scratch, including electronic circuit, PCB designing, firmware programming and manufacturing.

\item[ZTerm]\br
\textbf{ZTerm} is an open source terminal emulator with telnet/SSH2, multi-tab, Unicode support.
ZTerm is a cross platform software and implemented in Java.\br

\item[Stock analysis and visualization website]\br
A website displays realtime stocks information and charts.
I implemented a domain-specific language interpreter, technical indicators calculation and charts plotting in pure Javascript.\br

\item[Auto-trading system]\br
A machine learning based distributed futures auto-trading system.
The system receives realtime futures quotes and makes trading decisions base on historical data, the system is implemented in C, \CS, Python on Linux based GPU cluster.
\end{description}

\hr
\section*{Education}
\begin{description}
\item[National Taiwan University]\br
Master of Engineering, Computer Science\br
Parallel and Distributed Computing Laboratory\br
September 2005 -- June 2007

\item[National Central University]\br
Bachelor of Science, Major: Mathematics, Minor: Computer Science\br
September 2000 -- June 2005

\item[Tainan First Senior High School]\br
September 1997 -- June 2000
\end{description}

\hr
\section*{Patents}
\begin{itemize}
\item Systems and Methods for Sharing Conversion Data (US 20120162363 A1)
\end{itemize}

\hr
\section*{Publications}
\begin{itemize}
\item Computation and communication schedule optimization for data-sharing tasks on uniprocessor.\br
Jan-Jan Wu, \emph{En-Jan Chou}, Pangfeng Liu.\br
2009, Journal of Systems Architecture -- Embedded Systems Design, pp.363--372
\item Computation and communication schedule optimization for jobs with shared data.\br
\emph{En-Jan Chou}, Pangfeng Liu, Jan-Jan Wu.\br
2007, ICPADS, pp.1--8
\end{itemize}

\hr
\section*{Honors and Awards}
\begin{itemize}
\item Teaching-Assistant’s Merit Award, Dept. of CSIE in NTU, 2006
\item 3rd Place, National High School Programming Contest, 2000
\end{itemize}

\end{document}
